### 2014-03-28 LaTeX/Abstract.tex
mpsa abstract submitted
pushing stuff

Within the conflict literature there has been much disagreement about the relationship between civil wars, natural resources, and state economic performance. We find that this disagreement results from not accounting for the spatial disaggregation of conflict events within a country.  Other recent work has suggested that the location of civil conflicts within a state can lead to disparate outcomes in terms of conflict duration, state response, and the probability of rebel victory.  Drawing on these two literatures, we develop a theory to explain the economic consequences of civil conflict.

@@

We use subnational data on the spatial distribution of conflict, resources, and infrastructure to test the long-term impact of domestic conflict on state economic performance. To estimate the spatial distribution of conflict we use data from the PRIO Armed Conflict Location and Event Data and supplement this source with GDELT in more recent years. We combine the conflict location data with geospatial data on economic centers, natural resource locations, and infrastructure grids within the country to generate country-level spatial variables that approximate how far each conflict is from centers of interest for the government. We then use a hierarchical Bayesian model to estimate the effect of our spatially constructed variables on economic performance. By doing so, we are able to resolve some of the tensions in the literature regarding the relationship between economic performance and civil wars.

>>>>

% Within the conflict literature there has been much disagreement about the relationship between civil wars, natural resources, and state economic performance. We find that this disagreement results from not accounting for the spatial disaggregation of conflict events within a country.  Other recent work has suggested that the location of civil conflicts within a state can lead to disparate outcomes in terms of conflict duration, state response, and the probability of rebel victory.  Drawing on these two literatures, we develop a theory to explain the economic consequences of civil conflict.

% Our theoretical model states that the economic impacts of civil conflict is contingent on the conflict's location relative to major economic and labor resources within a state.

% We use subnational data on the spatial distribution of conflict, resources, and infrastructure to test the long-term impact of domestic conflict on state economic performance. To estimate the spatial distribution of conflict we use data from the PRIO Armed Conflict Location and Event Data and supplement this source with GDELT in more recent years. We combine the conflict location data with geospatial data on economic centers, natural resource locations, and infrastructure grids within the country to generate country-level spatial variables that approximate how far each conflict is from centers of interest for the government. We then use a hierarchical Bayesian model to estimate the effect of our spatially constructed variables on economic performance. By doing so, we are able to resolve some of the tensions in the literature regarding the relationship between economic performance and civil wars.

% Version submitted to MPSA:
Within the conflict literature there has been much disagreement about the relationship between civil wars, natural resources, and state economic performance. We find that this disagreement results from not accounting for the spatial disaggregation of conflict events within a country.

@@

We use subnational data on the spatial distribution of conflict, resources, and infrastructure to test the long-term impact of domestic conflict on state economic performance. To estimate the spatial distribution of conflict we use data from the PRIO Armed Conflict Location and Event Data. We combine the conflict location data with geospatial data on economic centers, natural resource locations, and infrastructure grids to generate spatial variables that approximate how far each conflict is from centers of interest. We then use a hierarchical Bayesian model to estimate the effect of the spatial variables on economic performance. By doing so, we are able to resolve some of the tensions in the literature regarding the relationship between economic performance and civil wars.

### 2014-03-28 LaTeX/RhodiumEmp.tex
manuscript edits
pushing stuff

Dependent variable: World Bank data GDP per capita growth

@@

	Conflict data: comes from PRIO Conflict Location Even Data

@@

Use simulations to determine substantive effects

>>>>

To measure economic performance we use annual percent change in GDP, which we collect from the World Development Indicators at the World Bank. We choose to focus on year over change in GDP because we expect conflicts proximate to major cities
to lead to reductions in growth not changes in levels.\footnote{Alternative measures of economic performance would have included changes in FDI inflows or changes in GDP per capita, in using either of these measures are results remain relatively the same.} Unlike much of the extant literature in constructing our dependent variable we focus on year over change instead of a ten year average. We believe this approach to be superior because it allows us to estimate the direct effect of the conflict on economic performance in that year. A ten-year average approach might hide important variation in our dependent variable that can be explained by the proximity of conflict to economic centers.

Our key independent variable on the location of conflicts come from the PRIO Conflict Site Dataset. This dataset contains geo-referenced armed conflict events from 1989 to 2008.\footnote{We only include examine the effect of internal armed conflicts.} A downside of this geo-referenced database is that every conflict-year is assigned a circular conflict zone, which leads to the dataset reporting that the conflict is covering more territory than actually affected. Crafting a more specfic approach to the spread of conflict would, however, eliminate important cases from our analysis. In total this dataset provides us with almost 800 geo-referenced conflict-year cases.

The key theory that we advance here is that the effects of conflict on economic performance are conditional on the proximity of those conflicts to major city centers. Thus a key part of the research here was determining major city centers by year. The only data source we found with enough geographical and temporal coverage on major cities was The World Alamanac. To gather data from these textbooks we hired several undergraduate students to code the major cities by country for each year of the Almanac from 1989 to 2008. Major cities are classified as those that have relatively large shares of a country's population and/or are economic centers. On average, for each country at least three major cities are identified in each year from 1989 to 2008. In figure \ref{fig:CityConfMap}, we show the geographic distribution of conflicts and cities.

\begin{figure}[ht]
	\centering
	\includegraphics[width=.9/textwidth]{CityConfMap-crop}
	\caption{This map illustrates the geographic distribution of all conflicts, according to the PRIO Conflict Site Dataset, and major cities listed in The World Almanac from 1989 to 2008. Countries for which no armed conflicts are recorded are shaded in grey.}
	\label{fig:CityConfMap}
\end{figure}

We restrict our sample to only those countries that are listed as having conflicts in the PRIO dataset. Specifically, this means that our analysis focuses on exploring variations in economic growth among countries currently engaged in internal armed conflict by the proximity of those conflicts to major cities. To do this we first calculate the distance between the centroid of each of the conflicts identified in the PRIO armed conflict dataset with the centroids of the city locations. Doing this between every city and every conflict

A key problem face in conducting this analysis is reconciling the unit of analysis for our independent and dependent variables. Our dependent variable is at the country-year and our independent variables are actaully at the conflict-country-year level.

@@

@@

\begin{figure}[ht]
	\centering
	\resizebox{.6\textwidth}{!}{\input{mod3CoefPlot.tex}}
\end{figure}
\FloatBarrier

Use simulations to determine substantive effects - SM

\begin{figure}[ht]
	\centering
	\resizebox{.8\textwidth}{!}{\input{mod3SimPlot.tex}}
\end{figure}
\FloatBarrier

### 2014-03-28 LaTeX/modCoefPlot.tex
pushing stuff

% Created by tikzDevice version 0.6.2 on 2014-03-28 11:43:10
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\fill[color=fillColor,fill opacity=0.00,] (0,0) rectangle (289.08,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

@@

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (214.52, 81.45) -- (214.54, 81.45);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (215.47,111.08) -- (216.65,111.08);

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (222.76,140.72) -- (255.30,140.72);

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (220.66,170.35) -- (235.55,170.35);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (209.97,199.99) -- (220.09,199.99);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (178.06,229.62) -- (213.50,229.62);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (166.20,259.25) -- (242.30,259.25);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

@@

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (214.52, 81.45) -- (214.53, 81.45);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (215.57,111.08) -- (216.56,111.08);

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (225.38,140.72) -- (252.69,140.72);

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (221.86,170.35) -- (234.36,170.35);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (210.79,199.99) -- (219.28,199.99);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (180.91,229.62) -- (210.65,229.62);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (172.32,259.25) -- (236.19,259.25);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
\definecolor[named]{fillColor}{rgb}{0.00,0.00,0.00}

@@

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (204.25,259.25) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (195.78,229.62) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (215.03,199.99) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (228.11,170.35) circle (  2.85);

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (239.03,140.72) circle (  2.85);

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (216.06,111.08) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (214.53, 81.45) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

@@

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.54, 79.97) --
	(214.54, 82.93);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.54, 81.45) --
	(214.52, 81.45);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.52, 79.97) --
	(214.52, 82.93);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\draw[color=drawColor,line width= 0.6pt,line join=round,] (216.65,109.60) --
	(216.65,112.57);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (216.65,111.08) --
	(215.47,111.08);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (215.47,109.60) --
	(215.47,112.57);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (255.30,139.24) --
	(255.30,142.20);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (255.30,140.72) --
	(222.76,140.72);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (222.76,139.24) --
	(222.76,142.20);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (235.55,168.87) --
	(235.55,171.83);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (235.55,170.35) --
	(220.66,170.35);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (220.66,168.87) --
	(220.66,171.83);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 0.6pt,line join=round,] (220.09,198.50) --
	(220.09,201.47);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (220.09,199.99) --
	(209.97,199.99);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (209.97,198.50) --
	(209.97,201.47);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line width= 0.6pt,line join=round,] (213.50,228.14) --
	(213.50,231.10);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (213.50,229.62) --
	(178.06,229.62);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (178.06,228.14) --
	(178.06,231.10);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 0.6pt,line join=round,] (242.30,257.77) --
	(242.30,260.74);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (242.30,259.25) --
	(166.20,259.25);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (166.20,257.77) --
	(166.20,260.74);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

@@

@@

@@

@@

@@

@@

>>>>

% Created by tikzDevice version 0.6.2 on 2014-03-28 11:37:36
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\fill[color=fillColor,fill opacity=0.00,] (0,0) rectangle (289.08,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

@@

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (214.53, 81.45) -- (214.55, 81.45);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (214.90,111.08) -- (215.62,111.08);

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (219.64,140.72) -- (243.62,140.72);
\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (214.53,170.35) -- (223.35,170.35);
\definecolor[named]{drawColor}{rgb}{0.99,0.57,0.45}
\definecolor[named]{fillColor}{rgb}{0.99,0.57,0.45}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (208.31,199.99) -- (214.71,199.99);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (200.24,229.62) -- (218.68,229.62);

\draw[color=drawColor,line width= 0.3pt,line join=round,fill=fillColor,fill opacity=0.30,draw opacity=0.30,] (170.81,259.25) -- (224.20,259.25);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

@@

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (214.53, 81.45) -- (214.55, 81.45);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (214.96,111.08) -- (215.57,111.08);

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (221.57,140.72) -- (241.69,140.72);
\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (215.24,170.35) -- (222.64,170.35);
\definecolor[named]{drawColor}{rgb}{0.99,0.57,0.45}
\definecolor[named]{fillColor}{rgb}{0.99,0.57,0.45}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (208.82,199.99) -- (214.20,199.99);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (201.72,229.62) -- (217.20,229.62);

\draw[color=drawColor,line width= 1.1pt,line join=round,fill=fillColor,] (175.10,259.25) -- (219.90,259.25);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}
\definecolor[named]{fillColor}{rgb}{0.00,0.00,0.00}

@@

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (197.50,259.25) circle (  2.85);

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (209.46,229.62) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.99,0.57,0.45}
\definecolor[named]{fillColor}{rgb}{0.99,0.57,0.45}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (211.51,199.99) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (218.94,170.35) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (231.63,140.72) circle (  2.85);

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (215.26,111.08) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.87,0.18,0.15}
\definecolor[named]{fillColor}{rgb}{0.87,0.18,0.15}

\draw[color=drawColor,line cap=round,line join=round,fill=fillColor,] (214.54, 81.45) circle (  2.85);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

@@

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.55, 79.97) --
	(214.55, 82.93);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.55, 81.45) --
	(214.53, 81.45);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.53, 79.97) --
	(214.53, 82.93);
\definecolor[named]{drawColor}{rgb}{0.21,0.56,0.75}
\definecolor[named]{fillColor}{rgb}{0.21,0.56,0.75}

\draw[color=drawColor,line width= 0.6pt,line join=round,] (215.62,109.60) --
	(215.62,112.57);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (215.62,111.08) --
	(214.90,111.08);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.90,109.60) --
	(214.90,112.57);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (243.62,139.24) --
	(243.62,142.20);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (243.62,140.72) --
	(219.64,140.72);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (219.64,139.24) --
	(219.64,142.20);
\definecolor[named]{drawColor}{rgb}{0.62,0.79,0.88}
\definecolor[named]{fillColor}{rgb}{0.62,0.79,0.88}

\draw[color=drawColor,line width= 0.6pt,line join=round,] (223.35,168.87) --
	(223.35,171.83);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (223.35,170.35) --
	(214.53,170.35);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.53,168.87) --
	(214.53,171.83);
\definecolor[named]{drawColor}{rgb}{0.99,0.57,0.45}
\definecolor[named]{fillColor}{rgb}{0.99,0.57,0.45}

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.71,198.50) --
	(214.71,201.47);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (214.71,199.99) --
	(208.31,199.99);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (208.31,198.50) --
	(208.31,201.47);
\definecolor[named]{drawColor}{rgb}{0.59,0.59,0.59}
\definecolor[named]{fillColor}{rgb}{0.59,0.59,0.59}

\draw[color=drawColor,line width= 0.6pt,line join=round,] (218.68,228.14) --
	(218.68,231.10);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (218.68,229.62) --
	(200.24,229.62);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (200.24,228.14) --
	(200.24,231.10);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (224.20,257.77) --
	(224.20,260.74);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (224.20,259.25) --
	(170.81,259.25);

\draw[color=drawColor,line width= 0.6pt,line join=round,] (170.81,257.77) --
	(170.81,260.74);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

@@

\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (147.62, 20.31) {-6};

@@

\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (169.93, 20.31) {-4};

@@

\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (192.24, 20.31) {-2};

@@

\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (214.56, 20.31) {0};

@@

\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (236.87, 20.31) {2};

@@

\node[color=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (259.18, 20.31) {4};
